%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}
	\cvpub{\textbf{Shikunova, A}. 2024. Forest Nenets monosyllabic shortening. Invited talk: Atelier de phonologie (SFL, CNRS \& Université Paris 8)}
	\cvpub{\textbf{Shikunova, A}. 2023. The three faces of Kazym Khanty schwa. Invited talk: Atelier de phonologie (SFL, CNRS \& Université Paris 8)}
\end{cvpubs}
\newpage

%-------------------------------------------------------------------------------
\cvsubsection{Conference Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub{\textbf{Shikunova, A.}. 2024. Length neutralization in Forest Nenets. Oral presentation: 21st Conference on Typology and Grammar for Young Scholars, Saint Petersburg, Russia.}
    
    \cvpub{\textbf{Shikunova, A. \& Kasenov, D.}. 2024. Second thought on the form and the substance of Russian vowel reduction. Poster presentation: RFP2024, Amiens, France.}
    
    \cvpub{\textbf{Shikunova, A.}. 2024. Positional weakness versus lack of prominence: Forest Nenets vowel alternations. Oral presentation: RFP2024, Amiens, France.}
    
    \cvpub{\textbf{Shikunova, A.}. 2023. Laryngeal contrast in L2 Russian of Forest Nenets speakers. Oral presentation: 20th Conference on Typology and Grammar for Young Scholars, Saint Petersburg, Russia.}
    
    \cvpub{\textbf{Shikunova, A. \& Belov, P.}. 2023. Forest Nenets vowel alternations and licensing of final nuclei. Oral presentation: 20th Conference on Typology and Grammar for Young Scholars, Saint Petersburg, Russia.}
    
    \cvpub{\textbf{Shikunova, A.}. 2023. The three faces of Kazym Khanty schwa. Oral presentation: WoSSP, Nantes, France.}
    
    \cvpub{\textbf{Shikunova, A.}. 2023. A case for stress as empty CVs: glide epenthesis in Moksha. Oral presentation: RFP2023, Nice, France.}
    
    \cvpub{\textbf{Shikunova, A.}. 2023. A case for stress as empty CVs: glide epenthesis in Moksha. Poster presentation: NAPhCxii, Montreal, Canada.}
    
    \cvpub{\textbf{Shikunova, A. \& Kasenov, D.}. 2023. Russian iotation: length is key. Poster presentation: NAPhCxii, Montreal, Canada.}
    
    \cvpub{\textbf{Shikunova, A.}. 2023. More than a small clause: Russian adverbial comparatives. Oral presentation: ConSOLE 31, Bielefeld, Germany.}
    
    \cvpub{\textbf{Shikunova, A. \& Sidorkina, D.}. 2022. Plural quantification in Kazym Khanty. Oral presentation: 19th Conference on Typology and Grammar for Young Scholars, Saint Petersburg, Russia.}
    
    \cvpub{\textbf{Shikunova, A. \& Rudnev, P.}. 2022. Idioms, NP position and control: evidence from Russian. Oral presentation: Typology of Morphosyntactic Parameters 2022, Moscow, Russia.}
    
    \cvpub{\textbf{Shikunova, A. \& Kasenov, D.}. 2022. Stress shift in Russian prepositional phrases: A strict CV approach. Oral presentation: FDSL15, Berlin, Germany.}
    
    \cvpub{\textbf{Shikunova, A}. 2022. Case and agreement puzzle in the Moksha debitive. Oral presentation: Syntax of Uralic Languages 4, online.}
    
    \cvpub{\textbf{Shikunova, A}. 2022. Mermaid construction: a case of Kazym Khanty. Poster presentation: ConSOLE 30, online.}
\end{cvpubs}
