%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Shikunova, A}. 2024. Quality-conditioned stress as length: glide epenthesis in Moksha. Submitted to Radical: A Journal of Phonology, 6, 31--73 [\href{https://radical.cnrs.fr/shikunova-quality-conditioned-stress-as-length-glide-epenthesis-in-moksha/}{pdf}]}

    \cvpub{\textbf{Shikunova, A}. 2023. There is no small clause in Russian phrasal comparatives. In Proceedings of ConSOLE XXXI, P. 134--150. [\href{https://www.universiteitleiden.nl/binaries/content/assets/geesteswetenschappen/lucl/sole/consolexxxi-proceedings.pdf}{pdf}]}
    
    \cvpub{\textbf{Shikunova, A}. 2023. Case and agreement puzzle in the Moksha debitive. In Journal of Uralic Linguistics, Vol. 2. No. 2. P. 194--213. [\href{https://www.jbe-platform.com/content/journals/10.1075/jul.00020.shi}{link}]}
    
    \cvpub{\textbf{Shikunova, A}. 2022. Mermaid construction: a case of Kazym Khanty. In Proceedings of ConSOLE XXX, P. 89--101. [\href{https://www.universiteitleiden.nl/binaries/content/assets/geesteswetenschappen/lucl/console30-proceedings.pdf}{pdf}]}
    
    \cvpub{\textbf{Shikunova, A. \& Rudnev, P.}. 2022. Idioms, NP position and control: Evidence from Russian. In Typology of Morphosyntactic Parameters 2022. Vol. 5. No. 1. P. 91--106. [\href{https://pavelrudnev.github.io/papers/tmp-paper.pdf}{pdf}]}
\end{cvpubs}

% %---------------------------------------------------------
%\cvsubsection{In Review}
%% %---------------------------------------------------------
%
%\begin{cvpubs}
%    \cvpub{\textbf{Shikunova, A}. 2023. Quality-conditioned stress as length: glide epenthesis in Moksha. Submitted to Radical: A Journal of Phonology [\href{https://lingbuzz.net/lingbuzz/007524/current.pdf}{pdf}]}
%\end{cvpubs}

% %---------------------------------------------------------
%\cvsubsection{In Prep}
%% %---------------------------------------------------------
%
%\begin{cvpubs}
%\small \color{black}
%    \cvpub{\textbf{Shikunova, A \& Kasenov, D.}. 2024. Second thought on the form and the substance of Russian vowel reduction}
%
%    \cvpub{Manuscript 2}
%\end{cvpubs}
%
% %---------------------------------------------------------
